---
title: "Draft Quarto document"
author: "Your Name"
format: html
---

## Header 1

```{r setup}
#| include: false
library(tidyverse)
library(here)
source(here("R/functions.R"))

```


## Prepare HR data
```{r}
#| eval: false
#| include: false

hr_data <- read_all("HR.csv.gz") %>%
  get_participant_id() %>% 
  summarise_by_datetime()


```{r}
ibi_data <- read_all("IBI.csv.gz")%>%
  get_participant_id() %>% 
  summarise_by_datetime()
```

```{r}
hr_data <- read_all("HR.csv.gz") %>%
  get_participant_id() %>% 
  summarise_by_datetime()
```

```{r}
ibi_data <- read_all("IBI.csv.gz") %>%
  get_participant_id() %>% 
  summarise_by_datetime()
```



#TEMP 
```{r}
Temp_data <- read_all("TEMP.csv.gz")%>%
  get_participant_id() %>% 
  summarise_by_datetime()
```

#BVP
```{r}
bvp_data <- read_all("BVP.csv.gz")%>%
  get_participant_id() %>% 
  summarise_by_datetime()

```
#EDA

```{r}
eda_data <- read_all("EDA.csv.gz")%>%
  get_participant_id() %>% 
  summarise_by_datetime()
```

## Process survey data: 

```{r}
survey_tidy <-here::here("data-raw/nurses-stress/survey-results.csv.gz") %>% 
  read() %>% 
  tidy_survey_dates()
survey_long <- survey_tidy %>% 
  survey_to_long()
  
```

